Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-04-09 paper/tex/sections/introduction.tex
remove results I and relabel

In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA. In Section~\ref{sec:resultsI}, we explore the detection of double compact objects with LISA analytically. In Section~\ref{sec:resultsII}, we present our main results for each type of DCO and variation of physical assumptions. In Section~\ref{sec:discussion} we discuss these results and finish with our conclusions in Section~\ref{sec:conclusion}.

>>>>

In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA. In Section~\ref{sec:results}, we present our main results for each type of DCO and variation of physical assumptions. In Section~\ref{sec:discussion} we discuss these results and finish with our conclusions in Section~\ref{sec:conclusion}.
